---
output: html_document
---
# Task 1:Prediction using Supervised ML
## SIMPLE LINEAR REGRESSION

### *By SRUSHTI S. SALI*

### Objective: To predict the score of a student based on the no. of study hours




***Reading the Data***

```{r}
url="http://bit.ly/w-data"
data_s<-read.csv(url)
head(data_s)
dim(data_s)
summary(data_s)
```


***Plotting the data points and computing correlation coefficient***

```{r}
X<-data_s$Hours
Y<-data_s$Scores
plot(X,Y,xlab="Hours Studied", ylab="Percentage Score", main = "Hours vs Percentage")
```

The scatter plot shows that there is strong positive correlation between the two variables.
```{r}
cor(X,Y)
```
The correlation coefficient is `r cor(X,Y)`, which indicates the strong positive correlation, i.e. more the no. of hours studied, more is the percentage score.


***Preparing the Data***

```{r}
dt<-sort(sample(nrow(data_s),nrow(data_s)*0.8))
data_train=data_s[dt,]
data_test=data_s[-dt,]
```


***Training the algorithm***

```{r}
model<-lm(Scores~Hours, data = data_train)
s=summary(model)
s
coefficients(model)
```

Thus,the model is (Percentage Score)= `r s$coefficients[1]`+`r s$coefficients[2]`(Hours Studied)

```{r}
s$r.squared
```

*The value of coefficient of determination is `r s$r.squared`, which indicates that the model is a good fit.*


***Scatter plot with the line of regression***

```{r, echo=FALSE}
plot(X,Y, xlab="Hours Studied", ylab="Percentage Score", main = "Hours vs Percentage", col="Red", pch=19)
abline(model, col="Black")
```


***Making Predictions***

```{r}
X_test=data_test[1]
Y_test=data_test[2]
Y_pred=predict(model,X_test)
data_p=data.frame("Actual"=Y_test, "Predicted_Sores"=Y_pred)
data_p
```


***Predicting score of a student who studied for 9.25 hours/day***

```{r}
h=data.frame(Hours=9.25)
predicted_score=predict(model,h)
predicted_score
```
**`r round(predicted_score,2)` is the predicted score of a student who studied for 9.25 hours/day.**

